---
title: "Project1"
author: "EzzahraFatmaMHD"
date: "1/23/2021"
output: html_document
---
#1-Code for reading in the dataset and/or processing the data  


```{r getdata}
# download file from web
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", destfile = "activity.zip", mode="wb")
# unzip data and read 
unzip("activity.zip")
#data <- read.csv(unzip("./repdata_data_activity.zip"))
data <- read.csv("activity.csv")

```
#2-Histogram of the total number of steps taken each day  


```{r }
library(dplyr)
library(ggplot2)
steps <- tapply(data$steps, data$date, FUN=sum, na.rm=TRUE)
qplot(steps,main = "total number of steps taken each day",  xlab = "number of step" 
      , ylab = "count"  )
```
#3-Mean and median number of steps taken each day  


```{r}
 mean(steps)

```  
 
```{r}

median(steps)

```  
  


#4-Time series plot of the average number of steps taken  

```{r}

avg  <- aggregate(x=list(steps_number=data$steps), by=list(interval=data$interval),
                             FUN=mean, na.rm=TRUE)
ggplot(avg, aes(x=interval, y=steps_number))+ geom_line()
```

#5-The 5-minute interval that, on average, contains the maximum number of steps  

```{r}
 avg[which.max(avg$steps_number),]

```

#6-Code to describe and show a strategy for imputing missing data  

##Missing  

```{r }
missing <- is.na(data$steps)
table(missing)
```
##Replacing the missings  

```{r }
replacewithmean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
complete_data <- data%>% group_by(interval) %>% mutate(steps= replacewithmean(steps))
head(complete_data)
```

#7-Histogram of the total number of steps taken each day after missing values are imputed  

```{r }
steps_with_no_missings <- tapply(complete_data$steps, complete_data$date, FUN=sum)
qplot(steps_with_no_missings,binwidth = 600, xlab="total number of steps taken each day")

```  

```{r }
mean(steps_with_no_missings)
```  

```{r ,echo=TRUE}
 median(steps_with_no_missings)

```  

#8-Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends  

##Procesisng data  

```{r }
which_day <- function(date) {
  day <- weekdays(date)
  if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
    return("weekday")
  else if (day %in% c("Saturday", "Sunday"))
    return("weekend")
  else
    stop("invalid date")
}
complete_data$date<- as.Date(complete_data$date)
complete_data$day <- sapply(complete_data$date, FUN=which_day)
averages <- aggregate(steps ~ interval + day, data=complete_data, mean)
head(averages)

```
##Comparing  

```{r }

ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
  xlab("5-minute interval") + ylab("Number of steps") +
  ggtitle("Comparison of Average Number of Steps in Each Interval")

```



